Quality Metrics for SKOS Vocabularies

### 2012-03-13 background.tex
added TODO to metrics

SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption. Established quality notions from closed-world systems, such as referential integrity or schema validation, don’t hold anymore, because the available information may be incomplete and facts that are not explicitly stated cannot be determined as true or false. While trust and provenance models for Web data are being developed~\cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets~\cite{Heath2011}.

@@

The quality of a given SKOS vocabulary can have a direct impact on the following application areas of controlled vocabularies: \todo{CM}{write a paragraph}

@@

\begin{itemize}
    \item Existing literature
    \item Mailing list discussions
    \item \ldots
\end{itemize}

>>>>

SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption. Established quality notions from closed-world systems, such as referential integrity or schema validation, don't hold anymore, because the available information may be incomplete and facts that are not explicitly stated cannot be determined as true or false. While trust and provenance models for Web data are being developed~\cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets~\cite{Heath2011}. \todo{CM}{check what the recent paper by Christophe Gueret is about.}

@@

\todo{CM}{argue why quality criteria beyond integrity conditions are needed; provide some good arguments and refer to the literature. The focus of this paragraph should be on quality in the controlled vocabulary domain...}

@@

\begin{itemize}
    \item Existing literature
    \item Mailing list discussions
    \item \ldots \todo{cm}{think about and finish this paragraph and lists.}
\end{itemize}
